Multi-level modelling with Openflexo/\FML - A contribution to the \mpc

### 2021-05-28 9-Relatedworks.tex
sync vers GitHub
add section 6.1 (basic modeling constructs)

A first description of process modeling as a multi-level modeling problem was proposed by \cite{lara2018refactoring} in the context of a catalogue of refactoring for multi-level models (in a simpler form with less constraints and requirements w.r.t. the challenge version). A solution is provided with MetaDepth~\citep{metadepth}, which supports modelling with any number of levels, dual ontological/linguistic typing and deep characterization through potency.

@@

More similar to us, \cite{deeptelos2019} use DeepTelos \citep{deeptelos2016}, an extension of the Telos language \citep{telos1990} in order to solve the process challenge. DeepTelos is based on the use of the PowerType \citep{atkinson2001essence} pattern. As with Openflexo and \FML, they do not use explicit (numbered) levels nor potency.

@@

\noteSM{Say something about constraints in \FML}

>>>>

A first description of process modeling as a multi-level modeling problem was proposed by \cite{lara2018refactoring} in the context of a catalogue of refactoring for multi-level models (in a simpler form with less constraints and requirements w.r.t. the challenge version). A solution is provided with MetaDepth~\citep{metadepth}, which supports modeling with any number of levels, dual ontological/linguistic typing and deep characterization through potency.

@@

More similar to us, \cite{deeptelos2019} use DeepTelos \citep{deeptelos2016}, an extension of the Telos language \citep{telos1990} in order to solve the process challenge. As with Openflexo and \FML, they do not use explicit (numbered) levels nor potency. However, DeepTelos is based on the use of the PowerType \citep{atkinson2001essence} pattern.

@@

%\noteSM{Say something about constraints in \FML} Bah... everybody does multilevel constraints.
